Future challenges for Research Software Engineering

### 2025-04-16 future_challenges_for_RSEng.tex

\subsection{How have academic Institutions transformed by then? ( Point 4 in the issue )}
\subsubsection{What do we want to have achieved}
We hope to see that universities use the presence of an RSE Department actively as a means to differentiate themselves from other universities.
We hope that the central RSE units have local RSE representatives, or even small RSE groups that handle tasks within a department to oversee specific projects[FIXME: cite group paper].
We also hope, that specialized clusters form, with certain RSE units specializing in certain tasks like data management, HPC, or visualization.
At universities which have them, we want to see, that researchers naturally accept them as part of their used services.

@@

\subsection{What are new tasks of RTPs?}
FG-NOTE: RSEs are one type of specialization of RTPs ins science. Do we see any other?

@@

FG-NOTE: By Nick. I've put it here, due to the relation with the RTP question.

>>>>

\subsection{How have academic Institutions transformed by then? ( Point 4 in the issue )}
\begin{whatis}{What do we want to have achieved}{acedemic}
We hope to see that universities use the presence of an RSE Department actively as a means to differentiate themselves from other universities.
We hope that the central RSE units have local RSE representatives, or even small RSE groups that handle tasks within a department to oversee specific projects[FIXME: cite group paper].
We also hope, that specialized clusters form, with certain RSE units specializing in certain tasks like data management, HPC, or visualization.
At universities which have them, we want to see, that researchers naturally accept them as part of their used services.
\end{whatis}

@@

\subsection{What are new tasks of RTPs?}
\begin{story}{text 1 }{text 2}
 FG-NOTE: RSEs are one type of specialization of RTPs ins science. Do we see any other?
\end{story}

@@

\begin{story}{text 1 }{text 2}
FG-NOTE: By Nick. I've put it here, due to the realtion with the RTP question.
\end{story}
